An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2019-12-13 jmiv.tex
Modify definitions in section 3; new figure for the ring-set

Let $d_{S}:\Omega \rightarrow \mathcal{R}$ be the Euclidean distance transformation with respect to shape $S$. The value $d_S(p)$ gives the Euclidean distance between $p$ and the closest pixel in $S$.

\begin{definition}[m-Ring Set]
Given a digital shape $S\in\Omega$, its distance transformation $d_S$ and natural numbers $m > 0$, the {\em $m$-ring set of $S$} is defined as
\begin{align*}
	\quad R_m(S) &:= R_m^-(S) \; \cup \; R_m^+(S) \\
	&:= \left\{ p \in \Omega \; | \; m-1 < d_S(p) \leq m \right\} \; \cup \;  \left\{ p \in \Omega \; | \; 	m-1 < d_{\overline{S}}(p) \leq m \right\}.
\end{align*}
\end{definition}

@@

Such set can be extremely large and its complete exhaustion is prohibitively expensive.  Instead, we explore a subset of it with the help of $n$-glued curves.

An oriented closed curve $C$ is a closed connected sequence of linels with a well-defined interior. A segment of $C$ is a connected subsequence $c \in C$ of its linels. We denote by $int(C)$ the interior of the shape bounded by curve $C$. Moreover, for a set of curves $\mathcal{C}$, we define $int(\mathcal{C}) = \bigcup_{C \in \mathcal{C}} int(C) $.

\begin{figure}[!h]
\center
	\subfloat[\label{}]{%
	\includegraphics[scale=0.2]{images/local_search/definitions/model-regions-square.eps}
	}\hspace{40pt}%
	\subfloat[\label{}]{%
	\includegraphics[scale=0.22]{images/local_search/definitions/glued-curve.eps}
	}%	
	\caption{The blue pixels in figure (a) illustrates a $2$-ring set, while the green pixels form its inner-pixel boundary. In figure (b) we highlight an element of set $\mathcal{G}_{11}(C_1,C_2)$. The curve segments of $C_1$ and $C_2$ are colored in red and green, while the junction linels in blue.}
\end{figure}

\begin{definition}[Glued Curve]
Given closed curves $C_1,C_2$ agreeing with some orientation $q$ such that $int(C_2) \subset int(C_1)$, a glued curve is a closed curve  $(c_1,\ell_1,c_2,\ell_2)$ with orientation $q$ and $c_1 \subset C_1, c_2 \subset C_2$. The linels $\ell_1,\ell_2$ are called junction linels.
\end{definition}

\begin{definition}[$n$-Glued Curve Set]
Given closed curves $C_1,C_2$ with same orientation, its set of $n$-glued curves is defined as
\begin{align*}
	\mathcal{G}_n(C_1,C_2) = \{ (c_1,\ell_1,c_2,\ell_2) \; | \; |c_2|=n \},
\end{align*}
\end{definition}

Let $S_O = ( S \cup R_1^+(S) ) $ and $S_I = ( S \setminus R_1^-(S) ) $, the neighborhood set to shape $S$ is defined as
\begin{align*}
	\mathcal{N}(S,N) = \bigcup_{1 \leq n \leq N} int \big(\; \mathcal{G}_{n}( \partial S_O, \partial S) \; \big) \cup int \big( \; \mathcal{G}_{n}(\partial S, \partial S_I) \; \big).
\end{align*}

Algorithm~\ref{alg:local-search} describes the local combinatorial process and Figure~\ref{fig:local-comb-square-results} presents the digital curve evolution when executing this algorithm for two different shapes with $N=50$.

@@

 \Input{A digital set $S$; the maximum length of glued curves $N$; the maximum number of iterations \MIt; and a stop condition \Tol}
 \BlankLine
 \Delta $\longleftarrow$ \Tol+1\;
 $i \longleftarrow 0$\;
 \While{ \It $<$ \MIt \bf{and} \Delta $>$ \Tol  }{
  	\For{$ X \in \mathcal{N}(S^{(i)},N) $}
	{
		\If{ $\hat{E}(X)$ $<$ $\hat{E}(X^\star)$ }
		{
			$X^\star \longleftarrow X$
		}
	}
	\It $\longleftarrow$ \It $+1$\;
	$S^{(i)} \longleftarrow X^\star$\;
	\Delta $\longleftarrow$ $\hat{E}(S^{(i-1)}) - \hat{E}(S^{(i)})$\;	
 }
 \caption{Local combinatorial optimization for elastica minimization.}
 \label{alg:local-search} 
\end{algorithm}

>>>>

Let $d_{S}:\Omega \rightarrow \mathcal{R}$ be the signed Euclidean distance transformation with respect to shape $S$. The value $d_S(p)$ gives the Euclidean distance between $p \notin S$ and the closest pixel in $S$. For points $p \in S$, $d_S(p)$ gives the distance between $p$ and the closest pixel not in $S$. The \emph{$m$-level set of $S$}

\begin{definition}[m-Ring Set]
Given a digital shape $S\in\Omega$, its signed distance transformation $d_S$ and natural number $m \neq 0$, the {\em $m$-ring set of $S$} is defined as
\begin{align*}
	\mathcal{R}_m(S) &:= \mathcal{L}_m \cup \mathcal{L}_{-m},
\end{align*}
where
\begin{align*}
	\mathcal{L}_m(S) &:= \left\{ \quad \begin{array}{cc}
		\left\{ p \in \Omega \; | \; m-1 < d_S(p) \leq m \right\} & , \quad m>0\\
		\left\{ p \in \Omega \; | \; m+1 > d_S(p) \geq m \right\} & , \quad m<0
		\end{array} \right.
\end{align*}
\end{definition}

@@

Such set can be extremely large and its complete exhaustion is prohibitively expensive.  Instead, we are going to use a subset of it.

\begin{definition}[$n$-neighborhood]
	Given a digital shape $S \in \Omega$, its $n$-neighborhood $\mathcal{N}_n(S)$ is defined as the set of digital shapes that can be built from $S$ by adding or removing a sequence of $n$ connected pixels in $R_1(S)$.
\end{definition}

\begin{figure}[!h]
\center
	\subfloat[\label{}]{%
	\includegraphics[scale=0.03]{images/local_search/definitions/R3.pdf}
	}\hspace{40pt}%
	\subfloat[\label{}]{%
	\includegraphics[scale=0.22]{images/local_search/definitions/glued-curve.eps}
	}%	
	\caption{The blue pixels in figure (a) illustrates a $3$-ring set. In figure (b) we highlight the contour of an element of set $\mathcal{N}_{11}$.}
\end{figure}

Algorithm~\ref{alg:local-search} describes the local combinatorial process and Figure~\ref{fig:local-comb-square-results} presents the digital curve evolution when executing this algorithm for two different shapes with $n=50$.

@@

 \Input{A digital set $S$; the neighborhood parameter $n$; the maximum number of iterations \MIt; and a stop condition \Tol}
 \BlankLine
 \Delta $\longleftarrow$ \Tol+1\;
 $i \longleftarrow 0$\;
 \While{ \It $<$ \MIt \bf{and} \Delta $>$ \Tol  }{
  	\For{$ X \in \mathcal{N}_n(S^{(i)}) $}
	{
		\If{ $\hat{E}(X)$ $<$ $\hat{E}(X^\star)$ }
		{
			$X^\star \longleftarrow X$
		}
	}
	\It $\longleftarrow$ \It $+1$\;
	$S^{(i)} \longleftarrow X^\star$\;
	\Delta $\longleftarrow$ $\hat{E}(S^{(i-1)}) - \hat{E}(S^{(i)})$\;	
 }
 \caption{Local combinatorial optimization for elastica minimization.}
 \label{alg:local-search} 
\end{algorithm}
